Incentivizing Exploration with Unbiased History

### 2018-10-27 3levelproofs.tex
3

\subsection{Case Analysis under Clean Events}
Now we assume the intersection of clean events happens. We will first
provide some helper lemmas for our case analysis.

@@

\begin{proof}
  The events $W_1^{a,s}$, $W_2^{a,s,1,t}$ for
  $t = q_a T_1- \GdT \sqrt{T_1\log(T)},...,q_a T_1 + \GdT
  \sqrt{T_1\log(T)}$ together imply that
\[
|\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_a T_1- \GdT \sqrt{T_1\log(T)}}} \leq \sqrt{\frac{4\log(T)}{q_a T_1}}.
\]
The last inequality holds when $T$ is larger than some constant.
\end{proof}

\begin{itemize}

\item For each arm $a$, define $\bar{\mu}_a$ to be the empirical mean of arm $a$ pulls in the first two levels. $W_1^{a,s}$ for $s=1,...,S$ and $W_3^{a,t}$ for $t \geq  (q_a T_1- \GdT \sqrt{T_1\log(T)})S$ together imply that
\[
|\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{S\left(q_a T_1- \GdT \sqrt{T_1\log(T)}\right)}} \leq \sqrt{\frac{4\log(T)}{S q_a T_1}} .
\]
The last inequality holds when $T$ is larger than some constant.

If there are at least $T_2$ pulls of arm $a$ in the first two levels, 
\[
|\bar{\mu}_a-\mu_a| \leq \sqrt{\frac{2\log(T)}{T_2}}. 
\]

\item % For each $a \in \{1,2\}$, $W_4$ implies that there exists $s_a$ such that $W_4^{s_a,a,high}$ and $W_4^{s_a,3-a,low}$ happen.
  The events $W_4^{s_a,a,high}$, $W_1^{s_a,a}$,
  $W_2^{s_a,a,t, q_aT_1}$ for
  $t = q_a T_1- \GdT \sqrt{T_1\log(T)}+1, ...,q_aT_1-1$ and
  $W_2^{s_a,a,q_aT_1,t}$ for
  $t= q_aT_1,...,q_a T_1+ \GdT \sqrt{T_1\log(T)}$ together imply that
\begin{align*}
\bar{\mu}_a ^{1,s_a} &\geq \mu_a + \left(q_aT_1 \cdot \frac{1}{\sqrt{q_aT_1}} - \GdT \sqrt{T_1\log(T)} \cdot \sqrt{\frac{2\log(T)}{ \GdT \sqrt{T_1\log(T)}}} \right) \cdot \frac{1}{q_a T_1+ \GdT \sqrt{T_1\log(T)}} \\
&> \mu_a + \frac{1}{4\sqrt{q_aT_1}}.
\end{align*}
The second to the last inequality holds when $T$ is larger than some constant.
Similarly, we also have
\[
\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1}}.
\]
\end{itemize}

\begin{proof}[Proof of Lemma~\ref{3levelbigcase}]
%   For each $s$-th first-level group and arm $a$, define
%   $\bar{\mu}_a^{1,s}$ to be the empirical mean of arm $a$ pulls in
%   this group. $W_1^{a,s}$, $W_2^{a,s,1,t}$ for
%   $ = q_a T_1- \GdT \sqrt{T_1\log(T)},...,q_a T_1- \GdT
%   \sqrt{T_1\log(T)}$ together imply that
% \[
% |\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_a T_1- \GdT \sqrt{T_1\log(T)}}} \leq \sqrt{\frac{4\log(T)}{q_a T_1}}.
% \]
% The last inequality holds as long as $T$ is larger than some
% constant.
  Observe that for any group $s$ in the first level, the empirical
  means satisfy
\[
\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{q_1T_1}} - \sqrt{\frac{4\log(T)}{q_2T_1}} \geq  \sqrt{\frac{4\log(T)}{q_1T_1}} + \sqrt{\frac{4\log(T)}{q_2T_1}}.
\]

% For each arm $a$, define $\bar{\mu}_a$ to be the empirical mean of arm
% $a$ pulls in the first two levels. $W_1^{a,s}$ for $s=1,...,S$ and
% $W_3^{a,t}$ for $t \geq (q_a T_1- \GdT \sqrt{T_1\log(T)})S$ together
% imply that
% \[
% |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{S\left(q_a T_1- \GdT \sqrt{T_1\log(T)}\right)}} \leq \sqrt{\frac{4\log(T)}{S q_a T_1}} .
% \]
% The last inequality holds when $T$ is larger than some constant.

>>>>

\subsection{Case Analysis under Clean Events}
Now we assume the intersection of clean events $W$ happens. We will
first provide some helper lemmas for our case analysis.

@@

\begin{proof}
  The events $W_1$ and $W_2^{a,s,1,t}$ for
  $t = q_a T_1- \GdT \sqrt{T_1\log(T)},...,q_a T_1 + \GdT
  \sqrt{T_1\log(T)}$ together imply that
\[
|\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_a T_1- \GdT \sqrt{T_1\log(T)}}} \leq \sqrt{\frac{4\log(T)}{q_a T_1}}.
\]
The last inequality holds when $T$ is larger than some constant.
\end{proof}

\begin{lemma}
  For each arm $a$, define $\bar{\mu}_a$ to be the empirical mean of
  arm $a$ pulls in the first two levels. If $W$ holds, then
  \[
    |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{4\log(T)}{S q_a T_1}} .
  \]
Furthermore, if there are at least $T_2$ pulls of arm $a$ in the first
two levels,
\[
|\bar{\mu}_a-\mu_a| \leq \sqrt{\frac{2\log(T)}{T_2}}. 
\]
\end{lemma}

\begin{proof}
The events $W_1^{a,s}$ for $s=1,...,S$ and $W_3^{a,t}$ for $t \geq  (q_a T_1- \GdT \sqrt{T_1\log(T)})S$ together imply that
  \[
    |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{S\left(q_a T_1- \GdT \sqrt{T_1\log(T)}\right)}} \leq \sqrt{\frac{4\log(T)}{S q_a T_1}} .
\]
The last inequality holds when $T$ is larger than some constant.
\end{proof}

\begin{lemma}
  For each $a \in \{1,2\}$, there exists a first-level group $s_a$
  such that
\[\bar{\mu}_a ^{1,s_a} > \mu_a + \frac{1}{4\sqrt{q_aT_1}} \quad \mbox{and, } \quad
\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1}}.
\]
\end{lemma}

\begin{proof}
  For each $a \in \{1,2\}$, $W_4$ implies that there exists $s_a$ such
  that both $W_4^{s_a,a,high}$ and $W_4^{s_a,3-a,low}$ happen.  The
  events $W_4^{s_a,a,high}$, $W_1^{s_a,a}$, $W_2^{s_a,a,t, q_aT_1}$
  for $t = q_a T_1- \GdT \sqrt{T_1\log(T)}+1, ...,q_aT_1-1$ and
  $W_2^{s_a,a,q_aT_1,t}$ for
  $t= q_aT_1,...,q_a T_1+ \GdT \sqrt{T_1\log(T)}$ together imply that
\begin{align*}
\bar{\mu}_a ^{1,s_a} &\geq \mu_a + \left(q_aT_1 \cdot \frac{1}{\sqrt{q_aT_1}} - \GdT \sqrt{T_1\log(T)} \cdot \sqrt{\frac{2\log(T)}{ \GdT \sqrt{T_1\log(T)}}} \right) \cdot \frac{1}{q_a T_1+ \GdT \sqrt{T_1\log(T)}} \\
&> \mu_a + \frac{1}{4\sqrt{q_aT_1}}.
\end{align*}
The second to the last inequality holds when $T$ is larger than some constant.
Similarly, we also have
\[
\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1}}.
\]
\end{proof}

\begin{proof}[Proof of Lemma~\ref{3levelbigcase}]
  Observe that for any group $s$ in the first level, the empirical
  means satisfy
\[
\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{q_1T_1}} - \sqrt{\frac{4\log(T)}{q_2T_1}} \geq  \sqrt{\frac{4\log(T)}{q_1T_1}} + \sqrt{\frac{4\log(T)}{q_2T_1}}.
\]
